\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{listings}

\lstset{basicstyle=\ttfamily, breaklines=true}

%opening
\title{README \\ Story Evolution Tracker}
\author{Violetta Avkhukova}
\date{August 26, 2016}

\begin{document}

\maketitle

\section{Certification}
I verify that I am the sole author of the programs contained in this folder, except where explicitly stated to the contrary. \\ \\ \\
\textbf{Signature:} \hspace*{6cm} \textbf{Date:} August 26, 2016

\section{Contents}
For source code contents, please refer to \lstinline|TABLE_OF_CONTENTS.txt|.

\section{Server Set-Up Instructions}
\begin{enumerate}
	\item Open the \lstinline|server| directory.
	\item Verify that the \lstinline|package.json| file is there.
	\item Verify that you have \lstinline|Node.JS| installed, versions \lstinline|4.5| and above.
	\item Run the command \lstinline|npm install| while in the \lstinline|server| directory. This will install all dependencies needed for the project.
	\item Once completed, run the server with the command \lstinline|npm start|.
	\item Open the web browser to \lstinline|http://localhost:3000/|.
\end{enumerate}

\section{Installing the Android Application}
\begin{enumerate}
	\item Put the file \lstinline|Story Evolution Tracker.apk| anywhere on your Android device, e.g. Downloads folder. Minimum supported Android version is 5.0.
	\item Open the file on your device. This will prompt to install it. Continue with installation.
	\item Open application.
\end{enumerate}

\section{Setting up Android code in Android Studio}
\begin{enumerate}
	\item Open Android Studio.
	\item Do File $\rightarrow$ New $\rightarrow$ Import Project...
	\item Select the directory \lstinline|StoryEvolutionTracker/Android/StoryEvolutionTracker| and follow any additional instructions.
	\item Build the project with Build $\rightarrow$ Make Project.
\end{enumerate}

\end{document}
